The error in Bayesian phylogenetic reconstruction when speciation co-occurs

### 2019-06-19 razzo-results.tex
Write down expected results

\section{Results}
Here we present the results as show in Fig.~\ref{fig:results}...

>>>>

\section{Results}

The inference error made for each of the parameter combinations
is shown in Fig.~\ref{fig:results}. For both extinction rates,
we find, as expected, that the error increases for increased $\nu$
or $q$. Also in line with our predictions, we find no difference
between the two extinction rates.
